---
title: "p8105_hw1_wx2233"
author: "Weijia Xiong"
date: 2019-09-12
output: github_document
---

# Problem1

## 1) Create a data frame
```{r apply the as.numeric, warning=FALSE, results='hide'}
library(tidyverse)
la_df = tibble(
  norm_samp = rnorm(8,mean = 0, sd = 1), #standard Normal distribution
  norm_samp_pos = norm_samp > 0,
  char_vec = c("a","b","c","d","e","f","g","h"),
  fac_vec = factor(c("small","small","small","middle","middle","middle","large","large"))
)

#mean
mean(pull(la_df,norm_samp))
mean(pull(la_df,norm_samp_pos))
mean(pull(la_df,char_vec))
mean(pull(la_df,fac_vec))

as.numeric(pull(la_df,norm_samp_pos))
as.numeric(pull(la_df,char_vec))
as.numeric(pull(la_df,fac_vec))
```

The mean of character vector and factor vector do not work.

* mean of random sample : `r mean(pull(la_df,norm_samp))`
* mean of logical vector : `r mean(pull(la_df,norm_samp_pos))`
* mean of character vector : `r mean(pull(la_df,char_vec))`
* mean of factor vector : `r mean(pull(la_df,fac_vec))`



When converting character to numeric, it does not work and all variables turn into NA.  
But for logical and factor variables, it works. Especially for logical variables, false becomes 0 and true becomes 1. When we try to take the mean, "FALSE" and "TRUE" turn to 0 and 1 so we can take the mean. And for factor variables, the result return the numeric codes that correspond to the factor level.

## 2) Convert and multiply
```{r convert and multiply}
log_to_num = as.numeric(pull(la_df,norm_samp_pos)) #convert into numeric
log_to_num * (pull(la_df,norm_samp)) #multiply

log_to_fac = as.factor(pull(la_df,norm_samp_pos))
log_to_fac * (pull(la_df,norm_samp))

fac_to_num = as.numeric(log_to_fac)
fac_to_num * (pull(la_df,norm_samp))
```

# Problem 2
## 1) Create a data frame
```{r create a dataframe for plot}
plot_df = tibble(
  x = rnorm(500, mean = 0, sd = 1), #standard normal distribution
  y = rnorm(500, mean = 0, sd = 1),
  log_xy = (x + y > 1),
  log_xy_num = as.numeric(log_xy),
  log_xy_fac = as.factor(log_xy)
)

```

* The size of the dataset:   
`r nrow(plot_df)` rows and `r ncol(plot_df)` columns.
* The mean of x is `r mean(pull(plot_df,x))` 
* The median of x is `r median(pull(plot_df,x))`  
* The standard deviation of x is `r sd(pull(plot_df,x))` 
* The proportion of cases for which x + y > 1 is `r round(sum(pull(plot_df,log_xy))/500,2)`

## 2) Create scatter plots
```{r yx_scatter log_color}
#First scatter plot with log_xy
ggplot(plot_df, aes(x = x, y = y,color = log_xy)) + geom_point()
ggsave("First scatter plot with log_xy.pdf")
```

```{r yx_scatter num_color}
#Second scatter plot with log_xy_num
ggplot(plot_df, aes(x = x, y = y,color = log_xy_num)) + geom_point()
```


```{r yx_scatterplot fac_color}
#Third scatter plot with log_xy_fac
ggplot(plot_df, aes(x = x, y = y,color = log_xy_fac)) + geom_point()
```

* The first plot and the third plot are same. And there are two color in each plot, represent that the factor classification:  "log_xy(or log_xy_fac)" is "TRUE" or "FALSE". The red area indicates that x+y>1 while the green area indicates the rest. We can see that the the red part is more than green. So these means that x+y>1 is more common than the other situation.
* In the second plot, the classifacation is "log_xy_num", which is a numeric vector. So the legend ranges from 0 to 1. But there are still two result of x+y>1. The black area indicates that x+y>1 while the blue area indicates the rest. This plot also means that x+y>1 is more common than the other situation.

